---
title: "2-nlp"
author: "mark koranda"
date: "12/21/2021"
output: html_document
---

NLP work is scattered, advanced through the 3 courses i taught, and RAs in between, from 2020--2022. The most recent implementations were consolidated for SR in 'v2...Rmd'.
That file, ballooning, is now split into 3, as v3:
v3 1-read_files.Rmd
v3 2-nlp.Rmd
v3 3-write_files.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# libraries

must manually run if this is not source.
```{r eval = FALSE}
library(tidyverse)
library(tidytext)
library(topicmodels)
library(tidyr)
library(reshape2)
library(stringi)

```

# manually select: 
recompile:
```{r eval = FALSE}
source("v3 1-read_file.Rmd")
```

or cached:
```{r eval = FALSE}
load("compiled_texts.rda")

```


# 2. (loaded data) inspect 

```{r}
df_wordns %>% 
  count(word,sort=TRUE) %>% 
  View
```


```{r}

df_wordns %>% 
  count(title,word, sort = TRUE) %>% 
  # ungroup %>% View
  group_by(title) %>% 
  mutate(wc=sum(n)) %>% 
  mutate(p = n/wc) %>%  
  group_by(title) %>% 
  slice_max(p,n=25) %>% 
  spread(key = word, value = p) %>% 
  View
```

# 3.tf_idf dist

```{r}
tidf <- df_wordns %>% 
  count(title,word, sort = TRUE) %>% 
  bind_tf_idf(word,title,n) %>%
  select(-n,-tf,-idf) %>% 
  spread(key= word, value = tf_idf)


distp <- tidf %>% 
  dist(upper = TRUE) %>% 
  as.matrix()

View(distp)

```

didn't get the numnums for the rarecounts, so here gos
```{r}
tiddy_f  <- df_wordns %>% 
  count(title,word, sort = TRUE) %>% 
  bind_tf_idf(word,title,n) 
```

```{r}

j_walk <- tiddy_f %>% 
  group_by(title) %>% 
  summarise(tf_idf = sum(tf_idf, na.rm=TRUE),
            mifdf = mean(tf_idf, na.rm=TRUE))

d2f <- j_walk %>% 
    left_join(df,.,by="title")
```

# 4. lda

```{r}

dtm <- df_wordns %>% 
  select(document = title,
                term=word) 

dtm1 <- cast_dtm(dtm,document,
                term,
         value = n)
```

```{r}
df_lda10 <- LDA(dtm1,
                k = 10,
              control = list(seed = 1234))
```

## projection scripts

```{r}

lda_wordtop <- . %>% 
  tidy(matrix = "beta")

lda_doctop <-  . %>% 
  tidy(matrix = "gamma")

lda_main <-  . %>% 
  tidy()

top_10words <- . %>%
  group_by(topic) %>%
  slice_max(beta, n = 10) %>% 
  ungroup() %>%
  arrange(topic, -beta)

top_10docs <- . %>%
  group_by(topic) %>%
  slice_max(gamma, n = 10) %>% 
  ungroup() %>%
  arrange(topic, -gamma)

doc_wide <- . %>%
  mutate(topic = paste0("topic", topic)) %>%
  pivot_wider(names_from = topic, values_from = gamma) %>% 
  filter(topic1 > .001 | topic2 > .001) %>%
  mutate(log_rat21 = log2(topic2 / topic1),
         log_rat31 = log2(topic3 / topic1))


```

## LDA 2tox

```{r}
df_lda2 <- LDA(dtm1, k = 2,
              control = list(seed = 1234))

```

```{r}

# lda2_word <- df_lda3 %>% lda_wordtop
# lda2_words_top <- lda3_word %>% top_10words

lda2_doc <- df_lda2 %>% lda_doctop
lda2_doc_wide <- lda2_doc %>% 
  mutate(topic = paste0("topic", topic)) %>%
  pivot_wider(names_from = topic, values_from = gamma) %>% 
  filter(topic1 > .001 | topic2 > .001)

# lda3_main <- df_lda3 %>% lda_main
```

```{r}
lda2_doc_wide %>% 
  ggplot(aes(x=topic1,y=topic2)) +
  geom_point(stat = "identity")
```

## LDA 3topics

```{r}
# set a seed so that the output of the model is predictable
# takes DocumentTermMatrix
df_lda3 <- LDA(dtm1, 
              k = 3, 
              control = list(seed = 1234))

```

docu topix


### df projections

```{r}

lda3_word <- df_lda3 %>% lda_wordtop
lda3_words_top <- lda3_word %>% top_10words

lda3_doc <- df_lda3 %>% lda_doctop
lda3_doc_wide <- lda3_doc %>% doc_wide

lda3_main <- df_lda3 %>% lda_main
```


### gg
```{r}
lda3_doc_wide %>% 
  ggplot(aes(x=log_rat21, y=topic3,size=topic3,fill=topic3))+
  geom_point(aes(colour=topic2))
```


## LDA10 topcis
```{r}
df_lda10 <- LDA(dtm1,
                k = 10,
              control = list(seed = 1234))
```

### df projections

```{r}

lda10_word <- df_lda10 %>% lda_wordtop
lda10_words_top <- lda10_word %>% top_10words

lda10_doc <- df_lda10 %>% lda_doctop
lda10_doc_wide <- lda10_doc %>% doc_wide
lda10_docs_top <- lda10_doc %>% top_10docs


lda10_main <- df_lda10 %>% lda_main


View(lda10_docs_top)
View(lda10_words_top)
lda10_docs_top %>% count(document) %>% arrange(-n)
```


### push-clean nchar
words top has annoying 1char words.
```{r}
tmp <- lda10_word %>% 
  filter(nchar(term)>2)

tmp <- tmp %>% top_10words
```


# CTM (wip)

```{r}
df_ctm4 <- CTM(dtm1, 4)
eg_ctm10 <- build_graph(df_ctm10,0.991)
```



# Save


```{r}
save(df_lda3,
     df_lda10,
     dtm,
     dtm1,
     df_wordns,
     df_ctm10,df_ctm4,
     #fns
     lda_wordtop,
     lda_doctop, lda_main, top_10words, top_10docs, doc_wide,
     
     file = "lda.rda")


```

