---
title: "3-write_files"
output: html_document
date: '2022-11-04'
---

NLP work is scattered, advanced through the 3 courses i taught, and RAs in between, from 2020--2022. The most recent implementations were consolidated for SR in 'v2...Rmd'.
That file, ballooning, is now split into 3, as v3:
v3 1-read_files.Rmd
v3 2-nlp.Rmd
v3 3-write_files.Rmd


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytext)
library(topicmodels)
library(tidyr)
library(reshape2)
library(stringi)

source("v3 1-read_files.Rmd")
source("v3 2-nlp.Rmd")

```

## Book 1 prep

```{r}
files  <- dir() 
```

select_files
```{r}
files <- files %>% 
  as.data.frame()  
colnames(b) <- "files"
files <- files %>% 
  mutate(files=as.character(files)) %>% 
  filter(grepl("txt",files)|
           grepl("md",files)) 
```

make df and header
- this feels cloojy but i've done it and it works.
```{r}

read_dir_txt <- function(files) {
  df <-readChar(files[1], 
                file.info(files[1])$size) %>% 
  data_frame(txt=.,title=files[1])
  
  for (name in files){
    a <- readChar(name, file.info(name)$size) %>% 
    data_frame(txt=.,title=name)
    df <- rbind(df,a)
  }
  return(df)
}
```

```{r}
book <- read_dir_txt("book v2.01.txt") %>% 
  .[1,]
```
```{r}
book_1 <- book %>% 
  unnest_tokens(word,txt)
book2 <- book_1 %>% 
  anti_join(get_stopwords()) %>% 
  count(word,sort = TRUE) %>% 
  mutate(doc = "book")

wons <- df_wordns %>% count(word,sort = TRUE) %>% 
  mutate(doc="corpus")
df_set <- rbind(book2,wons)
df_tidf <- df_set %>% 
  filter(n>1) %>% 
  bind_tf_idf(word,doc,n) %>% 
  filter(n>3)
compare <- df_tidf %>% 
  select(-n,-tf,-idf) %>% 
  group_by(word) %>% 
  mutate(cnt = length(doc)) %>% 
  filter(cnt>1) %>% 
  spread(key= "doc",value = "tf_idf")

compare <- compare %>% 
  mutate()
  
```

## Book 2 prep

currently a line breaks the csv 
```{r}
d2f %>% 
  mutate(text_slc = str_sub(txt,start=1L,end = 250)) %>% 
  select(-txt) %>% 
  write.csv(file="csv_from_the_df.csv")
```

```{r}
# make csv from the df

dft <- df %>% 
  mutate(txt = text) %>% 
  rm_md_head

df %>% 
  mutate(txt = text) %>% 
  mutate(text_slc = str_sub(txt,start=1L,end = 250)) %>% 
  select(-txt,-text) %>% 
  write.csv(file="csv_from_the_df.csv")

```

### in excel
A. created 2 vars:

```{r}
df %>% 
mutate(content_ratio = (wordcount_nonstop / wordcount)*100,
       linewt = lines*content_ratio # less useful
       linesize = wc / lines # new
)

```

manually coded files into three types
book 1 = 1
book 2 = 2
book 3 = 3

### read in
```{r}
files_2 <- read_csv("_prod-folder design_book_subset.csv")
```

match my subset,
filtering for book 2 (type==2).
(currently uses older database, unupdated)

```{r}
df2 <- files_2 %>% 
  select(title,
         type) %>% 
  left_join(df,.,by=c("title")) %>% 
  filter(type==2) # book 2
```

### pretty for md output.
```{r}
rm_filetype <- . %>% 
  filter(!grepl("md",title)) %>% 
  mutate(title_md = str_replace_all(title, ".txt|.Rmd",""),
         text = str_replace_all(text, "# ","### "))

df2 <- df2 %>% 
rm_filetype

```


### save
for tmp_vars_to_md
```{r}
save(df2,file = "book2df.rda")
```

